### 2008-03-01 SAiP/Module1/H3/doc/softwarearchitecture.tex
Introduction reinserted.

%A new Beer Web Store for specialty beers has the following main use
%case:
%\begin{quote}
%  The customer browses the beer catalogue for descriptions and
%  reviews. The customer selects appropriate beers for purchase and
%  these are added to his shopping basket. When the customer checks
%  out, payment is validated and he is presented with a receipt
%\end{quote}
%As a first step, the software architect of this systems has decided to
%use a layered architectural style (with clients, server, and a
%database in separate layers). He has decided that the communication to
%the database will be done via a Fa\c cade pattern. The system will be
%built in Java.

>>>>

A new Beer Web Store for specialty beers has the following main use
case:
\begin{quote}
  The customer browses the beer catalogue for descriptions and
  reviews. The customer selects appropriate beers for purchase and
  these are added to his shopping basket. When the customer checks
  out, payment is validated and he is presented with a receipt
\end{quote}
As a first step, the software architect of this systems has decided to
use a layered architectural style (with clients, server, and a
database in separate layers). He has decided that the communication to
the database will be done via a Fa\c cade pattern. The system will be
built in Java.
